Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-15 writeup/gz_hubble_data.tex
Re-iterate definition of lower-limit. Closes #102.

The criteria for determining whether a region of this space is single-valued,
and therefore correctable, is as follows: In each surface brightness and
redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and
using the best formal fit out of the three as measured by the sum of the
residuals. These fits are shown as the dashed black lines in
Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which
there is not a clear single-valued relationship between \ffeaturesz{} and
\ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any
data in which the polynomial fit has a slope less than this value is considered
\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
\ffeaturesrest{} value. Galaxies in this region are referred to as the
\emph{lower limit} sample. These regions are highlighted in blue in
Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently
high slopes to consider the relationship as single-valued; galaxies in these
regions are considered ``correctable'', and only these are used in measuring
the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface
brightness/redshift bins with at least 5 galaxies were considered; regions with
fewer than 5 galaxies are considered to have ``not enough information'' to
determine the \ffeaturesz{} and \ffeaturesrest{} relationship, colored gray in
Figure~\ref{fig:6a}.

>>>>

The criteria for determining whether a region of this space is single-valued,
and therefore correctable, is as follows: In each surface brightness and
redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and
using the best formal fit out of the three as measured by the sum of the
residuals. These fits are shown as the dashed black lines in
Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which
there is not a clear single-valued relationship between \ffeaturesz{} and
\ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any
data in which the polynomial fit has a slope less than this value is considered
\emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its
\ffeaturesrest{} value.  Galaxies in this region are referred to as the
\emph{lower limit} sample, because the most stringent correction available is
that the weighted \ffeatures{} is a lower limit to the true value.  These
regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white)
regions of the plot have sufficiently high slopes to consider the relationship
as single-valued; galaxies in these regions are considered ``correctable'', and
only these are used in measuring the parameters for the $\zeta$ function
(Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
5 galaxies were considered; regions with fewer than 5 galaxies are considered
to have ``not enough information'' to determine the \ffeaturesz{} and
\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.
